\vspace{6mm}\bfseries\LARGE Energy-Aware Planning-Scheduling for Autonomous Aerial Robots

### 2022-07-21 energy-planning.tex
proofreading (2)

The battery model predicts the battery SoC in the function of a given load at future time 
instants. There are multiple models in the literature~\cite{rao2003battery} with varying complexity {\color{black}and} accuracy %, and ease of implementation 
ranging from accurate but costly physical models~\cite{%moura2017battery,
marcicki2013design}, to abstract models~\cite{%xing2014state,
%he2011evaluation,
hinz2019comparison,mousavi2014various} %that have
{\color{black}with} compelling trade-offs in terms of the latter two. 
We model a Li-ion battery %of an aerial robot 
in-flight with an abstract ``Rint'' ECM in the literature~\cite{%he2011evaluation,
hinz2019comparison,mousavi2014various}.

@@

{\color{black}
The performance metric is $\Sigma_{t\in\mathcal{T}}(${\small $(w_1c_{i,1}(t)+w_2c_{i,2}(t)$}$)/$ $(${\small $|\mathcal{T}|\text{SoC}(t_f)$}$)$. If the initial battery SoC %at $t_0$ 
is seventy percent and both the parameters are weighted equally, i.e., ${\small w_1=w_2=}$ one half, \hyperref[fig:trajs-I-static]{I} would not be able to complete the flight, and \hyperref[fig:trajs-II-static]{II} has a performance metric of zero (i.e., the lowest configuration of parameters throughout the flight).
Nonetheless, performance metrics of \hyperref[fig:trajs-dyn-i]{i} and \hyperref[fig:trajs-dyn-ii]{ii} are 13.05 and 2.24, whereas the average detection and coverage quality is approx. 45 and 35 percent for \hyperref[fig:trajs-dyn-i]{i}, and 62 and 87 percent for \hyperref[fig:trajs-dyn-ii]{ii}.}
For both cases, scaling factors are derived empirically %, 
{\color{black}similarly to $\delta_i$ set to two hundred fifty}, 
the horizon $N$ is set to six seconds {\color{black} as in} relevant literature~\cite{gavilan2015iterative,%kang2009linear,
stastny2018nonlinear%,chao2011collision
}, order $r$ is three% (see Fig.~\ref{fig:il-abs})
, and the matrices $Q,R,Q_f$ are chosen such that the cost is merely 
squared control. {\color{black} $h$ is set to one-hundredth of a second and to one second for $\mathcal{K}$ and $\mathcal{T}$ respectively to allow sufficient precision and re-planning online.}
%\subsection{Algorithm evaluation}
%\subsubsection*{Periodic energy model}
%The figure
%{\color{black} Fig.~\hyperref[fig:stat]{6c}} %further 
%details the energy model's estimate (see detail view for \hyperref[fig:ener:static-I]{I}--\hyperref[fig:ener:static-II]{II}) on an initial slice of the model (${\hat{y}}$), power ($\Upsilon$), and period ($T$). % We motivate this choice again with Fig.~\ref{fig:il-abs}, where the power spectrum subfigure shows that 3 frequencies are adequate. 
%The {\color{black} right} detail of \hyperref[fig:ener:static-I]{I} illustrates the evolutions of the state $\mathbf{q}$ in time, concluding that approximately two periods suffice for a consistent %state 
%estimate. %With non-periodic signals, we observed that the estimator estimates primarily the first state $\alpha_0$ and it neglects the others. It hence approximates the non-periodicity with a linear model.

>>>>

The battery model predicts the battery SoC as a function of a given load at future time 
instants. There are multiple models in the literature~\cite{rao2003battery} with varying complexity {\color{black}and} accuracy %, and ease of implementation 
ranging from accurate but costly physical models~\cite{%moura2017battery,
marcicki2013design}, to abstract models~\cite{%xing2014state,
%he2011evaluation,
hinz2019comparison,mousavi2014various} %that have
{\color{black}with} compelling trade-offs in terms of the latter two. 
We model a Li-ion battery %of an aerial robot 
in-flight with an abstract ``Rint'' ECM in the literature~\cite{%he2011evaluation,
hinz2019comparison,mousavi2014various}.

@@

{\color{black}
The performance metric is $\Sigma_{t\in\mathcal{T}}(${\small $(w_1\tilde{c}_{i,1}(t)+w_2\tilde{c}_{i,2}(t)$}$)/$ $(${\small $|\mathcal{T}|\text{SoC}(t_f)$}$)$ with {\small $\tilde{c}_{i,j}\hspace*{-.4ex}:=\hspace*{-.4ex}(c_{i,j}\hspace*{-.3ex}-\hspace*{-.3ex}\underline{c}_{i,j})/(\overline{c}_{i,j}\hspace*{-.3ex}-\hspace*{-.3ex}\underline{c}_{i,j})$}. If the initial battery SoC %at $t_0$ 
is seventy percent and both the parameters are weighted equally, i.e., {\small $w_1\hspace*{-.3ex}=\hspace*{-.3ex}w_2\hspace*{-.3ex}=\hspace*{-.3ex}$} one half, \hyperref[fig:trajs-I-static]{I} would not be able to complete the flight, and \hyperref[fig:trajs-II-static]{II} has a performance metric of zero (i.e., the lowest configuration of parameters throughout the flight).
Nonetheless, performance metrics of \hyperref[fig:trajs-dyn-i]{i} and \hyperref[fig:trajs-dyn-ii]{ii} are 13.05 and 2.24, whereas the average detection and coverage quality is approx. 45 and 35 percent for \hyperref[fig:trajs-dyn-i]{i}, and 62 and 87 percent for \hyperref[fig:trajs-dyn-ii]{ii}.}
For both cases, scaling factors are derived empirically %, 
{\color{black}similarly to $\delta_i$ set to two hundred fifty}, 
the horizon $N$ is set to six seconds {\color{black} as in} relevant literature~\cite{gavilan2015iterative,%kang2009linear,
stastny2018nonlinear%,chao2011collision
}, order $r$ is three% (see Fig.~\ref{fig:il-abs})
, and the matrices $Q,R,Q_f$ are chosen such that the cost is merely 
squared control. {\color{black} $h$ is set to one-hundredth of a second and to one second for $\mathcal{K}$ and $\mathcal{T}$ respectively to allow sufficient precision and re-planning online.}
%\subsection{Algorithm evaluation}
%\subsubsection*{Periodic energy model}
%The figure
%{\color{black} Fig.~\hyperref[fig:stat]{6c}} %further 
%details the energy model's estimate (see detail view for \hyperref[fig:ener:static-I]{I}--\hyperref[fig:ener:static-II]{II}) on an initial slice of the model (${\hat{y}}$), power ($\Upsilon$), and period ($T$). % We motivate this choice again with Fig.~\ref{fig:il-abs}, where the power spectrum subfigure shows that 3 frequencies are adequate. 
%The {\color{black} right} detail of \hyperref[fig:ener:static-I]{I} illustrates the evolutions of the state $\mathbf{q}$ in time, concluding that approximately two periods suffice for a consistent %state 
%estimate. %With non-periodic signals, we observed that the estimator estimates primarily the first state $\alpha_0$ and it neglects the others. It hence approximates the non-periodicity with a linear model.
